Quantifying the home ground advantage with `hyper2` and `hyper3` objects

### 2024-10-18 inst/home_advantage.Rmd
formatting of time taken to run without cache
mention hyper3

---
title: "Quantifying the home ground advantage with `hyper2` objects"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

To cite the `hyper2` package in publications, please use @hankin2017_rmd
(takes about fifteen minutes to run without cache).  Here I analyse a
small synthetic dataset for home ground advantage, then go on to
discuss a dataset presented by Agresti.  But first, the smallest
nontrivial example is a 2x2 case:

>>>>

---
title: "Quantifying the home ground advantage with `hyper2` and `hyper3` objects"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

(takes about fifteen minutes to run without cache).

To cite the `hyper2` package in publications, please use
@hankin2017_rmd.  Here I analyse a small synthetic dataset for home
ground advantage, then go on to discuss a dataset presented by
Agresti.  But first, the smallest nontrivial example is a 2x2 case:
